---
title: "Summer Products Sales Analysis on Wish.com"
subtitle: "Data Visualisation Project"
author: "Zahra Hashemi"
date: "25 Jan 2024"
format: 
  revealjs:
    transition: slide
    slide-number: c
editor: visual
warnings: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(GGally)
library(ggExtra)
library(stringr)
library(rmarkdown)
library(knitr)
```

```{r, include=FALSE}
products <- readr::read_csv("data/summer_products_with_rating_and_performance_2020_08.csv", show_col_types = FALSE)
```

```{r, include=FALSE}
products |>
  mutate(has_urgency_banner = ifelse(is.na(has_urgency_banner), 0, has_urgency_banner)) |>
  mutate(urgency_text = ifelse(is.na(urgency_text), " ", urgency_text)) -> products
```

::: slide
## Introduction

In this project, we are planning to analyze summer-related products as of July 2020. The dataset consists of a snapshot of some of the products available on the e-commerce platform Wish.com.

<br>
The dataset is sourced from [data.world](https://data.world/jfreex/summer-products-and-sales-performance-in-e-commerce-on-wish).
:::

## dataset

``` r
observations: 1,573 variables: 43

part of the table:

$ title                     <chr> "2020 Summer Vintage Flamingo Print  Pajamas Set Casual...", ...
$ price                     <dbl> 16.00, 8.00, 8.00, 8.00, 2.72, 3.92, 7.00, 12.00,
$ retail_price              <dbl> 14, 22, 43, 8, 3, 9, 6, 11, 84, 22, 5, 8, 6, 42, 2, 81, 10, 25, 9,
$ product_id                <chr> "5e9ae51d43d6a96e303acdb0", "58940d436a0d3d5da4e95a38",...
$ units_sold                <dbl> 1e+02, 2e+04, 1e+02, 5e+03, 1e+02, 1e+01, 5e+04, 1e+03,
$ uses_ad_boosts            <dbl> 0, 1, 0, 1, 1, 0, 0, 0, 1, 0, 0, 1, 1, 0, 1, 0, 0, 1,
$ rating                    <dbl> 3.76, 3.45, 3.57, 4.03, 3.10, 5.00, 3.84, 3.76, 3.47, 3.60, 3.4..
$ tags                      <chr> "Summer,Fashion,womenunderwearsuit,printedpajamasset,womencasualshort,Wo..", ..
$ product_color             <chr> "white", "green", "leopardprint", "black", "yellow", "navyblue", ...
$ shipping_option_name      <chr> "Livraison standard", "Livraison standard", "Livraison standard",..
$ shipping_option_price     <dbl> 4, 2, 3, 2, 1, 1, 2, 3, 2, 2, 2, 2, 1, 2,
$ shipping_is_express       <dbl> 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,..
$ has_urgency_banner        <dbl> 1, 1, 1, 0, 1, 0, 0, 0, 1, 0, 1, 1, 0, 0, 0, 0, 0, 1, 0,
$ urgency_text              <chr> "Quantité limitée !", "Quantité limitée !", "Quantité limitée !" ...
$ origin_country            <chr> "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN", "CN",...
$ merchant_name             <chr> "zgrdejia", "sarahouse", "hxt520", "allenfan", "happyhorses",
$ merchant_info_subtitle    <chr> "83 % avis positifs (17,752 notes)", "86 % avis positifs (295 notes)"…
$ merchant_rating           <dbl> 4.128521, 3.899673, 3.989831, 4.020435, 4.001588, 3.507692, 4.076516, 3...
$ product_url                  <chr> "https://www.wish.com/c/5e9ae51d43d6a96e303acdb0", "https://www.wish.com/c/58940d436…
```

## Color Trends in Summer Sales

Summer colors or again popular colors?

```{r}
your_custom_color_vector <- c(
  "black" = "#000000",
  "white" = "#FFFFFF",
  "gray" = "#808080",
  "purple" = "#800080",
  "blue" = "#0000FF",
  "red" = "#FF0000",
  "green" = "#008000",
  "pink" = "#FFC0CB",
  "yellow" = "#FFFF00",
  "orange" = "#FFA500",
  "navyblue" = "#000080",
  "multicolor" = "#A0A0A0", 
  "light green" = "#90EE90",
  "wine red" = "#722F37",
  "armygreen" = "#4B5320",
  "khaki" = "#F0E68C",
  "floral" = "#FFC0CB", 
  "rosered" = "#FF033E",
  "beige" = "#F5F5DC",
  "skyblue" = "#87CEEB"
)
```

```{r}
products |>
  mutate(product_color = tolower(product_color),
         product_color = ifelse(product_color %in% c("gray", "grey"), "gray", product_color),
         product_color = ifelse(product_color %in% c("wine red", "winered"), "wine red", product_color)) |>
  group_by(product_color) |>
  summarise(total_units_sold = sum(units_sold)) |>
  drop_na() |>
  top_n(20, total_units_sold) |>
  ggplot(aes(x = total_units_sold, y = reorder(product_color, total_units_sold), fill = product_color)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_text(aes(label = total_units_sold), vjust = 0.5, color = "black", nudge_x = 100000) +  # adjust nudge_x manually
  labs(title = "Units Sold by Color", x = "Total Units Sold", y = "Color") +
  scale_x_continuous(labels = scales::comma_format()) +
  scale_fill_manual(values = your_custom_color_vector)
```

Still, black and white are popular colors, even in summer!

## Exploring Global Satisfaction

A Comparative View of Product Ratings by Country of Origin

```{r}
sample_size = products |>
  group_by(origin_country) |>
  summarize(num=n())

products |>
  left_join(sample_size) |>
  drop_na(origin_country) |>
  mutate(origin_count = paste0(origin_country, "\n", "n=", num)) |>
  ggplot(aes(x = origin_count, y = rating, fill = factor(origin_country))) +
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, alpha = 0.5) +      # geom_jitter(height = 0, width = 0.001)     ## previous code
  labs(title = "Distribution of Ratings by Country of Origin",
    x = "Country of Origin",
    y = "Rating") +
  scale_fill_brewer(palette = "Pastel1", name = "Country of Origin", 
                    labels = c("CN" = "China", 
                                 "SG" = "Singapore", 
                                 "US" = "United States", 
                                 "VE" = "Venezuela",
                                 "AT" = "Austria", 
                                 "GB" = "United Kingdom (Great Britain)"))
```

## Trust in Ratings

High Correlation Between Merchant Ratings and Positive Reviews

```{r}
products |>
  filter(grepl("^\\d", merchant_info_subtitle)) |>
  select(merchant_info_subtitle, merchant_rating) |>
  mutate(percentage_value = as.numeric(str_extract(merchant_info_subtitle, "^\\d+"))) -> part_of_products

correlation <- cor(part_of_products$merchant_rating, part_of_products$percentage_value, use = "complete.obs")

part_of_products |>
  ggplot(aes(x = merchant_rating, y = percentage_value)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "red") + 
  geom_text(aes(label = sprintf("correlation = %.2f", correlation)), x = 2.5, y = 100, hjust = 0, vjust = 1, color = "red") +  # Correlation
  labs(
    title = "Merchant Rating vs Percentage of Positive Reviews",
    x = "Merchant Rating",
    y = "Percentage of Positive Reviews",
    caption = "Data filtered based on merchant_info_subtitle starting with a number. Correlation coefficient shown in red."
  )
```

## Express vs Economy

The Price of Speed in Shipping Choices

```{r}
ggplot(subset(products, !(shipping_option_name %in% c( "การส่งสินค้ามาตรฐาน", "الشحن القياسي", "ការដឹកជញ្ជូនតាមស្តង់ដារ"))),
       aes(x = shipping_option_name, y = shipping_option_price, fill = factor(shipping_is_express))) +
  stat_summary(fun = "mean", geom = "col") +
  labs(title = "Average Shipping Price by Company and Express Status",
       x = "Shipping Company",
       y = "Average Shipping Price",
       fill = "Express Shipping") +
  scale_fill_manual(labels = c("Not Express", "Express"), values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Reputation and Quality

Examining the Link Between Merchant Rating and Product Satisfaction

```{r}
correlation <- cor(products$rating, products$merchant_rating, use = "complete.obs")
products |>
  ggplot(aes(x = merchant_rating, y = rating)) +
  geom_point(alpha = 0.6) +  
  geom_smooth(method = "lm", color = "blue") + 
  annotate("text", x = max(products$merchant_rating), y = min(products$rating), 
           label = paste("Pearson r:", round(correlation, 2)), hjust = 2, vjust = -0.5, color='red') +
  labs(title = "Product Rating vs. Merchant Rating",
       x = "Merchant Rating",
       y = "Product Rating") 
```

The correlation is not very strong though! Other factors are involved too for sure

## TODO

* Doing analysis on tags, such as categorizing by men and women

## Thank you for your attention!

