

The dataset is sourced from data.world:
  >> https://data.world/jfreex/summer-products-and-sales-performance-in-e-commerce-on-wish


In this project, we are planing to analyse the summer-related products, as of July 2020. The dataset consists of a snapshot of some of the products available on the e-commerce platform Wish.com.



```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


```{r}
products <- readr::read_csv("data/summer_products_with_rating_and_performance_2020_08.csv", show_col_types = FALSE)
```


>> Some explanations about the dataset:

>> retail price:

retail price, or reference price in other stores/places. Used by the seller to indicate a regular value or the price before discount.

>> uses_ad_boosts

Whether the seller paid to boost his product within the platform (highlighting, better placement or whatever)

>> rating_count

Total number of ratings of the product

>> badges_count

Number of badges the product or the seller have
```{r}
products |>
  group_by(badges_count) |>
  summarise(count = n(), percentage = round((n() / nrow(products)) * 100, 2))
```
>> badge_local_product

A badge that denotes the product is a local product. Some people may prefer buying local products rather than. (boolean)

>> badge_product_quality

Badge awarded when many buyers consistently gave good evaluations 1 means Yes, has the badge

>> tags

'tags will not be a good evaluation'

```{r}
products |>
  summarise(n_distinct(tags), nrow(products))
```
>> product_color  (102 distinct colors)

```{r}
products |>
  distinct(product_color)
```
>> product_variation_size_id

The column is not tidy. It requires some adjustments and cleaning.
E.g. we can see both 'M' and 'M.' in this column.
```{r}
products |>
  distinct(product_variation_size_id)
```
>> product_variation_inventory

????????????????????????????????????????????????????

>> shipping_option_price 

change the column name to shipping_price

>> inventory_total 

??????????????????????????????????????????????????????

>> has_urgency_banner

could have been a good measure!
```{r}
products |>
  distinct(has_urgency_banner)
```
>> origin_country

```{r}
products |>
  distinct(origin_country)
```
theme and crawl_month are already useless because our data was limited to summer and the month July.
```{r}
products |>
  distinct(theme)
```


>> Things TODO

rating_count ~ units_sold

countries_shipped_to ~ units_sold 
(because if seller increases the number of countries for shipping, number of demands also increases.)

merchant_has_profile_picture could also have some effects :?

>> Best sellers

We can have a discussion on sellers too. Best sellers based on number of units sold, rating, mean of products price comparing with mean of retail prices, mean of discounts, mean of product ratings and so on. 

>> Best products

Based on ratings (mean and median, also we can define a range for bad and good rating and have some analysis on good and bad ratings too), mean of prices and retail prices, units solds and so on.






