

The dataset is sourced from data.world:
  >> https://data.world/jfreex/summer-products-and-sales-performance-in-e-commerce-on-wish


In this project, we are planing to analyse the summer-related products, as of July 2020. The dataset consists of a snapshot of some of the products available on the e-commerce platform Wish.com.



```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


```{r}
products <- readr::read_csv("data/summer_products_with_rating_and_performance_2020_08.csv", show_col_types = FALSE)
```


>> Some explanations about the dataset:

>> retail price:

retail price, or reference price in other stores/places. Used by the seller to indicate a regular value or the price before discount.

>> uses_ad_boosts

Whether the seller paid to boost his product within the platform (highlighting, better placement or whatever)

>> rating_count

Total number of ratings of the product

>> badges_count

Number of badges the product or the seller have
```{r}
products |>
  group_by(badges_count) |>
  summarise(count = n(), percentage = round((n() / nrow(products)) * 100, 2))
```
>> badge_local_product

A badge that denotes the product is a local product. Some people may prefer buying local products rather than. (boolean)

>> badge_product_quality

Badge awarded when many buyers consistently gave good evaluations 1 means Yes, has the badge

>> tags

'tags will not be a good evaluation'

```{r}
products |>
  summarise(n_distinct(tags), nrow(products))
```




>> Things TODO

rating_count ~ units_sold






